Solutions to Integer Programming from Quantum Annealing

### 2020-05-28 paper/main.tex
Added links to GH issues

\begin{abstract}
 While quantum computing proposes promising solutions to computational problems not accessible with classical approaches, due to current hardware constraints, most quantum algorithms are not yet capable of computing systems of practical relevance, and classical counterparts outperform them.
 To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
 For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
 This work presents the formalism of how to map ILP problems to the annealing architectures.
 It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
 We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
  %Conclusion: What do these findings mean to us?
  [Rephrase] We need better hardware to challenge heuristic solvers but we identified how to optimize hardware.
  %Perspectives: What should be done next?
  [Rephrase] Better understand correlations and localizations and improve simulation to scale to larger problems.

@@

\alert{[Formulate: Decoherence \& Localization]}
Hardware suffers from...
For this reason one is not guaranteed to find optimal solutions

\alert{[Formulate: Simulations]}
To understand findings and limitations, we mimic the hardware

@@

\begin{figure}[htb]
 \centering
 \includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
 \caption{asdf}
 \label{fig:anneal_schedule}
\end{figure}

@@

Mention long coherence time asymptote to right value.

Scan coherence time, match to DWave.

Some more discussion about short coherence time and why it makes sense?

Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence.
In this regard, a very short T1 is pushing the systems toward a classical annealing model.
The absence of any dephasing is then the best-case quantum annealing model.
Consequently, the difference in outcome would trace back to this coherence being present.

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{./figures/coherence.pdf}
 \caption{asdf}
 \label{fig:prob_mi}
\end{figure}

@@

%----------------------------------------------------------------------------------------
\subsubsection{Other Simulation Details}
%----------------------------------------------------------------------------------------
Temperature
Initial wave function choices
RK tolerance

@@

Things to do:

Compute dwave mutual information

Study ground state degeneracy by plotting distribution of states.

@@

@@

Link to GitHub.

@@

We thank x, y, z...

@@

C.K. drank a lot of coffee.

@@

%========================================================================================
\bibliography{qilp}
%========================================================================================

>>>>

\newcommand{\ghissue}[2]{
 \noindent\fbox{\parbox{0.49\textwidth}{
   \alert{[#1]}%
   \\%
   \href{https://github.com/cchang5/quantum\_linear\_programming/pull/#2}{See GitHub issue #2}}%
 }}
}

\begin{abstract}
 While quantum computing proposes promising solutions to computational problems not accessible with classical approaches, due to current hardware constraints, most quantum algorithms are not yet capable of computing systems of practical relevance, and classical counterparts outperform them.
 To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
 For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
 This work presents the formalism of how to map ILP problems to the annealing architectures.
 It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
 We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.

 \ghissue{Finalize abstract}{13}

@@

\ghissue{Decoherence \& Localization}{14}

\ghissue{Simulations}{15}

@@

\begin{figure}[htb]
 \centering
 \includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
 \caption{
  Anneal schedules for amplitudes of initial Hamiltonian (solid) and final Hamiltonian (dashed) are displayed for a complete anneal schedule.
  Different colors represent different offesets: advanced (blue), default (black) and delayed (red).
 }
 \label{fig:anneal_schedule}
\end{figure}

@@

\ghissue{Decoherence section}{#16}

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{./figures/coherence.pdf}
 \caption{To be updated}
 \label{fig:prob_mi}
\end{figure}

@@

%----------------------------------------------------------------------------------------
\subsubsection{Other Simulation Details}
%----------------------------------------------------------------------------------------

\ghissue{Simulation details}{#18}

@@

\ghissue{Finalize results}{#19}

@@

\ghissue{Conclusion}{#20}

@@

\ghissue{Data availability}{#21}

@@

\ghissue{Acknowledgements}{#22}
We thank x, y, z...

@@

\ghissue{Author contributions}{#23}
C.K. drank a lot of coffee.

@@

%========================================================================================
\bibliography{qilp}
\ghissue{References}{#24}
%========================================================================================
